What We Eval in the Shadows

### 2021-08-10 paper/main.tex
minor

\begin{wrapfigure}{r}{5.8cm}
\begin{tabular}{c}
{\hspace{-25mm}\includegraphics[width=0.7\textwidth]{package_size_loaded_distribution}}
\end{tabular}
\caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}

@@

The expressions passed to \eval vary widely. In order to categorize them, let us
use a minimization function $min(e)$ which for a given expression $e$ returns a
normal form that abstracts incidental details allowing the reader to focus on
the structure of the evaluated code. The minimization function performs constant
folding of arithmetic and string expressions for base operators, e.g.
$min(\c{1+1})=\c{V}$, value simplification, $min(\c{c(1,2,3+2)})=\c{V}$,
variable absorption, $min(\c{x+y})=\c{X}$, function absorption,
$min(\c{g(f(x),h(z))})=\c{F(F(X))}$ and a number of other simplifications.
Table~\ref{tab:minimizedexpressions} gives the 10 most frequent forms; \#sites
and \%sites are, respectively, the number and ratio of sites receiving arguments
of that form; \#packages is the number of packages with that form; \#operations
is the median number of instructions performed by the interpreter; and \%envir
is the ratio of sites that evaluate in a function environment. The example
column shows one sample expression $e$ that normalizes to the particular form.

>>>>

\begin{wrapfigure}{r}{6.2cm}
\begin{tabular}{c}
{\hspace{-25mm}\includegraphics[width=0.8\textwidth]{package_size_loaded_distribution}}
\end{tabular}
\caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}

@@

The expressions passed to \eval vary widely. We categorize expressions using a
minimization function which abstract some of the incidental details of
expressions and return a ``shape'' that can be used to group similar \evals. The
function $min(e)$ which for a given expression $e$ returns a normal form. Normal
forms use \c V to stand in for values occurring in expression, \c X stands in
for variables, and \c F stands for functions. The function performs constant
folding of arithmetic and string expressions over base operators, for instance
$min(\c{1+1})$ simplifies to $\c{V}$, on the ground that addition of values
likely returns a value. Value simplification takes $min(\c{c(1,2,3+2)})$ to
$\c{V}$ as a complex vector containing values is a value. Variable absorption
has $min(\c{x+y})$ becomes $\c{X}$, this motivated by the fact that addition is
not an ``interesting'' operation, and that \c X stands in for any number of
variable lookups. Function absorption simplifies nested functions to keep an
abstraction of the nesting $min(\c{g(f(x),h(z))})=\c{F(F(X))}$. There are other
simplifications, the full list is in our artifact. It is worth mentioning that
these simplifications are heuristics, in R \c{1+1} is not necessary \c 2. The
addition operator can be redefined, but it typically isn't or at least not in a
way that would invalidate arithmetic.

Table~\ref{tab:minimizedexpressions} gives the 10 most frequent forms; \#sites
and \%sites are, respectively, the number and ratio of sites receiving arguments
of that form; \#packages is the number of packages with that form; \#operations
is the median number of instructions performed by the interpreter; and \%envir
is the ratio of sites that evaluate in a function environment. The example
column shows one sample expression $e$ that normalizes to the particular form.
